---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# school.epi.abm

<!-- badges: start -->
[![R-CMD-check](https://github.com/UCLA-PHP/school.epi.abm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/UCLA-PHP/school.epi.abm/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of school.epi.abm is to implement an agent-based model of COVID infection and mitigation dynamics in K-6 schools, as described in 
<https://doi.org/10.3389/fpubh.2023.856940>.

## Installation

You can install the development version of school.epi.abm like so:

``` r
# install.packages("devtools") # if not already installed
devtools::install_github("UCLA-PHP/school.epi.abm")
```

## Loading the package

After instalation, you can load the package with the `library()` function:
```{r}
library(school.epi.abm)
```


## Examples

The graphical user interface (GUI) for the model can be run using the following command:

```{r example, eval=FALSE}

shiny::runApp()

```

The GUI is also deployed at <https://agent-based-models.shinyapps.io/RegionalCOVIDSchoolSimulation/>.

The model can also be run directly from the R command line using the following commands:

```{r, eval = FALSE}

library(school.epi.abm)

simulation_outputs = run_simulation(
  n_schools = 10,
  verbose = TRUE)

```

We can summarize and visualize the results as follows: 

```{r, eval = FALSE}

average_class_data_by_day = summarize_records(simulation_outputs$class_records)

plot1a = plot1_plotly(
  class_records,
  plot3_ymax = 6)

print(plot1a)

```

```{r, eval = FALSE}
analyze_results(simulation_outputs)

```

The subfolder `inst/extdata` contains the analysis script `ABM results loop.R`, which can be used to loop over a table of input conditions (specified in that script as the tibble `conditions_to_cross`) and reproduce the tables in the corresponding article (<https://doi.org/10.3389/fpubh.2023.856940>).
